---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# I Know How You Drive (ikhyd)

<!-- badges: start -->
<!-- badges: end -->

The goal of ikhyd is to make the analysis process of telematics data easier.

## Installation

You can install the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("issactoast/ikhyd")
```

## Example

### Calibation of telematics data

Using `calibrate_telematics` function, you can obtain a calibarated longitudinal, latitudinal acceleration data and GPS data from telematics data.

```{r example}
library(ikhyd)

## basic example code
sample_data_path <- system.file("extdata", "sample_trip.csv",
                                package = "ikhyd")

calibration_result <- calibrate_telematics(sample_data_path)

acc_data <- calibration_result$acc_data
gps_data <- calibration_result$gps_data
```


- Result (acc_data)
    - x: Lateral acceleration
    - y: Longditudinal acceleration
```{r}
head(acc_data)
```


- Result (gps_data)
    - x: Longditude
    - y: Latitude
```{r}
head(gps_data)
```

